\documentclass[10pt, a4paper]{article}

% Packages:
\usepackage[
    ignoreheadfoot, % set margins without considering header and footer
    top=1 cm, % seperation between body and page edge from the top
    bottom=1 cm, % seperation between body and page edge from the bottom
    left=1 cm, % seperation between body and page edge from the left
    right=1 cm, % seperation between body and page edge from the right
    footskip=1.0 cm, % seperation between body and footer
    % showframe % for debugging
]{geometry} % for adjusting page geometry
\usepackage{titlesec} % for customizing section titles
\usepackage{tabularx} % for making tables with fixed width columns
\usepackage{array} % tabularx requires this
\usepackage[dvipsnames]{xcolor} % for coloring text
\definecolor{primaryColor}{RGB}{0, 79, 144} % define primary color
\usepackage{enumitem} % for customizing lists
\usepackage{fontawesome5} % for using icons
\usepackage{amsmath} % for math
\usepackage[
    pdftitle={Abdul Rahman (abdxdev) - Resume},
    pdfauthor={Abdul Rahman},
    pdfcreator={Abdul Rahman},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref} % for links, metadata and bookmarks
\usepackage[pscoord]{eso-pic} % for floating text on the page
\usepackage{calc} % for calculating lengths
\usepackage{bookmark} % for bookmarks
\usepackage{lastpage} % for getting the total number of pages
\usepackage{changepage} % for one column entries (adjustwidth environment)
\usepackage{paracol} % for two and three column entries
\usepackage{ifthen} % for conditional statements
\usepackage{needspace} % for avoiding page brake right after the section title
\usepackage{iftex} % check if engine is pdflatex, xetex or luatex
\usepackage{hyperref}
\usepackage{url}
\usepackage[normalem]{ulem} % for better underlines

% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    % \usepackage[T1]{fontenc} % this breaks sb2nov
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

% Some settings:
\AtBeginEnvironment{adjustwidth}{\partopsep0pt} % remove space before adjustwidth environment
\pagestyle{empty} % no header or footer
\setcounter{secnumdepth}{0} % no section numbering
\setlength{\parindent}{0pt} % no indentation
\setlength{\topskip}{0pt} % no top skip
\setlength{\columnsep}{0cm} % set column seperation
\makeatletter
\let\ps@customFooterStyle\ps@plain % Copy the plain style to customFooterStyle
\patchcmd{\ps@customFooterStyle}{\thepage}{
    % \color{gray}\textit{\small Abdul Rahman - Page \thepage{} of \pageref*{LastPage}}
    \color{gray}\textit{}
}{}{} % replace number by desired string
\makeatother
\pagestyle{customFooterStyle}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{
    % left space:
    -1pt
}{
    % top space:
    0.3 cm
}{
    % bottom space:
    0.2 cm
} % section title spacing

\renewcommand\labelitemi{$\circ$} % custom bullet points
\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.1 cm,
        parsep=0.1 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0.4 cm + 10pt
    ]
}{
    \end{itemize}
} % new environment for highlights

\newenvironment{highlightsforbulletentries}{
    \begin{itemize}[
        topsep=0.1 cm,
        parsep=0.1 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=10pt
    ]
}{
    \end{itemize}
} % new environment for highlights for bullet entries

\newenvironment{onecolentry}{
    \begin{adjustwidth}{
        0.2 cm
    }{
        0.2 cm
    }
}{
    \end{adjustwidth}
} % new environment for one column entries

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
} % new environment for two column entries

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}
}{
    \par\kern\topsep
} % new environment for the header

\newcommand{\createpointblock}[5]{
    \begin{twocolentry}{
        \textit{#2}

        \textit{#4}}
        \textbf{#1}

        \textit{#3}
    \end{twocolentry}

    \vspace{0.1 cm}
    \begin{onecolentry}
        \begin{highlights}
            #5
        \end{highlights}
    \end{onecolentry}
}

% \newcommand{\placelastupdatedtext}{% \placetextbox{<horizontal pos>}{<vertical pos>}{<stuff>}
%   \AddToShipoutPictureFG*{% Add <stuff> to current page foreground
%     \put(
%         \LenToUnit{\paperwidth-2 cm-0.2 cm+0.05cm},
%         \LenToUnit{\paperheight-1.0 cm}
%     ){\vtop{{\null}\makebox[0pt][c]{
%         \small\color{gray}\textit{Last updated in September 2024}\hspace{\widthof{Last updated in September 2024}}
%     }}}%
%   }%
% }%

% save the original href command in a new command:
\let\hrefWithoutArrow\href

% new command for external links:
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{\ifthenelse{\equal{#2}{}}{}{\textcolor{black}{\uline{#2}}\raisebox{.15ex}{}}}}
% \renewcommand{\href}[2]{\hrefWithoutArrow{#1}{\ifthenelse{\equal{#2}{}}{ }{#2 }\raisebox{.15ex}{\footnotesize \faExternalLink*}}}

\begin{document}
\newcommand{\AND}{\unskip
	\cleaders\copy\ANDbox\hskip\wd\ANDbox
	\ignorespaces
}
\newsavebox\ANDbox
\sbox\ANDbox{}

% \placelastupdatedtext
\begin{header}
	\textbf{\fontsize{24 pt}{24 pt}\selectfont Abdul Rahman}

	\vspace{0.3 cm}

	\normalsize
	\mbox{\hrefWithoutArrow{https://www.google.com/maps/place/Lahore,+Pakistan}{\color{black}{\footnotesize\faMapMarker*}\hspace*{0.13cm}Lahore, Pakistan}}
	\kern 0.25 cm
	\AND
	\kern 0.25 cm
	\mbox{\hrefWithoutArrow{mailto:abdulrahman.abd.dev@gmail.com}{\color{black}{\footnotesize\faEnvelope}\hspace*{0.13cm}abdulrahman.abd.dev@gmail.com}}
	\kern 0.25 cm
	\AND
	\kern 0.25 cm
	\mbox{\hrefWithoutArrow{tel:+92-320-1002771}{\color{black}{\footnotesize\faPhone*}\hspace*{0.13cm}+92 320 1002771}}
    \\
	\mbox{\hrefWithoutArrow{https://abd-dev.studio/}{\color{black}{\footnotesize\faLink}\hspace*{0.13cm}abd-dev.studio}}
	\kern 0.25 cm
	\AND
	\kern 0.25 cm
	\mbox{\hrefWithoutArrow{https://github.com/abdxdev}{\color{black}{\footnotesize\faGithub}\hspace*{0.13cm}github.com/abdxdev}}
	\kern 0.25 cm
	\AND
	\kern 0.25 cm
	\mbox{\hrefWithoutArrow{https://linkedin.com/in/abdxdev}{\color{black}{\footnotesize\faLinkedinIn}\hspace*{0.13cm}linkedin.com/in/abdxdev}}
\end{header}

% \section{About Me}

%     \begin{onecolentry}
%         I am a software developer and designer with expertise in building efficient, user-friendly applications across different platforms. With a focus on problem-solving and creative design, I enjoy crafting innovative solutions that make a difference.
%     \end{onecolentry}

%     \vspace{0.2 cm}

%     \begin{onecolentry}
%         The boilerplate content was inspired by \href{https://github.com/dnl-blkv/mcdowell-cv}{Gayle McDowell}.
%     \end{onecolentry}

\section{Education}

    \createpointblock{University of Engineering and Technology, Lahore}{Sept 2023 - Present}{BS in Computer Science}{}
    {%
        \item CGPA: 3.55/4.0
        % \item \textbf{Coursework:} Data Structures, Algorithms, Operating Systems, Computer Networks, Database Systems, Software Engineering, Artificial Intelligence, Machine Learning
    }

\section{Technical Skills}

    % \renewcommand{\arraystretch}{} % Adjusts row spacing
    % \setlength{\extrarowheight}{0.11 cm} % Adds extra height between rows
    % \begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{0.25\linewidth}>{\raggedright\arraybackslash}X}
    %     \textbf{Programming Languages:}    & Python, C++, C, JavaScript, TypeScript, SQL, C\#.                                      \\
    %     \textbf{Frameworks and Libraries:} & Django, Flask, Streamlit, .NET, Tkinter, Reflex, Flet, React, Next.js.                 \\
    %     \textbf{DevOps Tools:}             & Docker, Git, GitHub, GitLab, Vercel, Render, Azure.                                    \\
    %     \textbf{Databases:}                & PostgreSQL, MySQL, SQLite, Microsoft SQL Server, Access.                               \\
    %     \textbf{Markup and Style:}         & HTML, CSS, Tailwind CSS, Markdown, LaTeX.                                              \\
    % \end{tabularx}

    \begin{itemize}
        \item \textbf{Programming Languages:} Developed robust applications and scripts using Python, C++, C, JavaScript, TypeScript, SQL, and C\#, gaining strong problem-solving and algorithmic skills across multiple paradigms.
        \item \textbf{Frameworks and Libraries:} Built scalable web and desktop solutions with Django, Flask, Streamlit, .NET, Tkinter, Reflex, Flet, React, and Next.js, learning to architect full-stack systems and user interfaces.
        \item \textbf{DevOps Tools:} Automated deployments and version control using Docker, Git, GitHub, GitLab, Vercel, Render, and Azure, which taught me best practices in CI/CD and collaborative development.
        \item \textbf{Databases:} Designed and managed relational databases with PostgreSQL, MySQL, SQLite, Microsoft SQL Server, and Access, deepening my understanding of data modeling, querying, and optimization.
        \item \textbf{Markup and Style:} Created responsive and visually appealing interfaces using HTML, CSS, Tailwind CSS, Markdown, and LaTeX, enhancing my skills in web design and technical documentation.
    \end{itemize}

\section{Experience}

    \createpointblock{Backend Developer}{2023 - Present}{Freelance (Self Employed)}{}
    {%
    \item Developed backend systems for clients using Django, Flask, and .NET, including REST APIs, web applications, and automation scripts.
    }
    
    \vspace{0.2 cm}
    
    \createpointblock{Graphic Designer}{2021 - 2023}{Freelance (Self Employed)}{}
    {%
        \item Directed and designed marketing materials for clients, including UI/UX design, branding, and social media content.
    }
    
\section{Projects}

% VSCode Extensions
\textbf{VSCode Extensions}
\begin{highlights}
    \item \textbf{\href{https://github.com/abdxdev/ai-regex-search}{AI Regex Search}} (TypeScript, VSCode API, Gemini): Built a VS Code extension that lets users generate regular expressions from natural language and insert them directly into the search tool.
    \item \textbf{\href{https://github.com/abdxdev/10x-Pretender}{10x Pretender}} (TypeScript, VSCode API): Developed a VS Code extension that simulates realistic typing from clipboard or AI-generated code, making code demos and presentations more engaging.
    \item \textbf{\href{https://github.com/abdxdev/AI-LaTeX-Helper}{AI LaTeX Helper}} (TypeScript, VSCode API, Gemini): Created an extension that converts plain English descriptions into LaTeX equations, simplifying the process of writing math in LaTeX.
\end{highlights}

\vspace{0.2 cm}

% Desktop Applications
\textbf{Desktop Applications}
\begin{highlights}
    \item \textbf{\href{https://github.com/abdxdev/Context-Menu-Plugin-Manager}{Context Menu Plugin Manager}} (Python, Flet): Developed a desktop app that allows users to manage and extend Windows context menus with custom Python plugins for enhanced directory actions.
    \item \textbf{\href{https://github.com/abdxdev/AMOS}{AMOS}} (C\#, WinUI 3): Designed a modern restaurant management system enabling seamless order processing and administration for customers, managers, and admins.
    \item \textbf{\href{https://github.com/abdxdev/prize-bond-finder}{Prize Bond Finder}} (Python): Created a user-friendly desktop tool for efficiently managing, searching, and tracking prize bonds with a simple interface.
\end{highlights}

\vspace{0.2 cm}

% Web Applications
\textbf{Web Applications}
\begin{highlights}
    \item \textbf{\href{https://github.com/abdxdev/odoo-lens}{Odoo Lens}} (TypeScript, Next.js): Built a web app that augments Odoo ERP with advanced analytics, search, and management tools for business insights.
    \item \textbf{\href{https://github.com/abdxdev/Markdown-badge-generator}{Markdown Badge Generator}} (Python, Streamlit): Developed a web tool for instantly generating and customizing markdown badges for project READMEs.
    \item \textbf{\href{https://github.com/abdxdev/Recurrence-Relation-Solver}{Recurrence Relation Solver}} (Python, Streamlit, Sympy): Built a web tool for solving and visualizing mathematical recurrence relations using symbolic computation.
\end{highlights}

% \vspace{0.2 cm}

% % Utilities & Tools
% \textbf{Utilities \& Tools}
% \begin{highlights}
%     \item \textbf{\href{https://github.com/abdxdev/Terminal-Based-Rich-Text-Editor}{Terminal Based Rich Text Editor}} (C++): Engineered a fast terminal editor featuring autosuggestions, undo/redo, and customizable shortcuts for efficient text editing.
%     \item \textbf{\href{https://github.com/abdxdev/Console-Utility}{Console Utility}} (C++): Developed a C++ library offering advanced console text formatting and cursor control utilities for terminal applications.
% \end{highlights}

\end{document}